---
title       : Developing Data Products
subtitle    : Week 4
author      : Prabhu Thaipulley
date        : 8th May 2017
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap, quiz]           # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
output:
  revealjs::revealjs_presentation:
    incremental: true
    theme: sky
    center: true
  reveal_options:
      slideNumber: true
      previewLinks: true   
  
--- 

# Storm Database Explorer

```{r, echo=FALSE}
library(data.table)
library(rCharts)
library(reshape2)

dt <- fread('./Data/events.agg.csv')
dt.agg.year <- dt[, list(Count=sum(COUNT), Injuries=sum(INJURIES), Fatalities=sum(FATALITIES)), by=list(YEAR)]
```


--- 

## Between 1950 and 2011 severe weather events caused at least

 - `r format(sum(dt$FATALITIES), big.mark=' ')` deaths
 - `r format(sum(dt$INJURIES), big.mark=' ')` injuries
 - $`r format(round((sum(dt$PROPDMG) + sum(dt$CROPDMG)) / 1000), big.mark=' ')` billion worth of damage
 

--- 

## Now you can prepare yourself using Storm Database Explorer



 - state of the art user interface*
 - high quality data**
 - fast and reliable***
 - 100% Open source 

---

*** =foo

- * If you really determined there is a chance you'll find worse.
- ** There is small chance it could be worse.
- *** It works. Most of the time.

--- &custom .custom

## ... and it can generate cool plots


```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F}
data <- melt(dt.agg.year[, list(YEAR=YEAR, Injuries=Injuries, Fatalities=Fatalities)], id='YEAR')
populationImpact <- nPlot(value ~ YEAR, group = 'variable', data = data[order(-YEAR, variable, decreasing = T)], type = 'stackedAreaChart', dom = 'populationImpact')
        
populationImpact$chart(margin = list(left = 100))
populationImpact$yAxis( axisLabel = "Affected", width = 80)
populationImpact$xAxis( axisLabel = "Year", width = 70)
        
populationImpact
```

--- &custom .custom

## Are you interested?

- visit us on shinyapps.io [Week 4 Project Presentation and documents](https://tsprabhu.shinyapps.io/dpw4_shinyapp/)
- fork on GitHub ([Developing Data Products Week 4 Project Assignment](https://github.com/prabhut/Data-Products-Week-4))






